Enriching Object Detection with 2D-3D Registration\\and Continuous Viewpoint Estimation

### 2014-11-14 egpaper_final.tex
8 pages
line breaker in title
number

\def\cvprPaperID{****} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

@@

%%%%%%%%% TITLE
\title{Enriching Object Detection with 2D-3D Registration and Continuous Viewpoint Estimation}
%\title{Enrich Object Detection : 2D-3D registration and continuous viewpoint estimation}

@@

\section{Conclusion}
\label{conclusion}
\input{conclusion}

>>>>

\def\cvprPaperID{2349} % *** Enter the CVPR Paper ID here
\def\httilde{\mbox{\tt\raisebox{-.5ex}{\symbol{126}}}}

@@

%%%%%%%%% TITLE
\title{Enriching Object Detection with 2D-3D Registration\\and Continuous Viewpoint Estimation}
%\title{Enrich Object Detection : 2D-3D registration and continuous viewpoint estimation}

@@

\section{Conclusion}
\label{conclusion}
\vspace{-.2cm}
\input{conclusion}

### 2014-11-14 experiments.tex
8 pages
number

\paragraph{Results.}
Tab.~\ref{tab:3dobject} gives the corresponding results, comparing our
method to two recent state-of-the-art baselines, the aspect layout
model (ALM~\cite{Xiang12}), and the
DPM-VOC+VP~\cite{Pepik12}. Fig.~\ref{fig:3dobject} gives corresponding
qualitative results.

@@

To show such ability, we evaluate our method on the PASCAL3D+
dataset~\cite{Xiang14}. This dataset augments PASCAL 2012 images with
high quality viewpoint annotations thus is ideal to measure pose
estimation. The dataset proposes new metric called Average Viewpoint
Precision (AVP) where it measures the area under viewpoint precision
and detection recall curve. The viewpoints is measured by azimuth
similarity. If the distance between predicted azimuth and ground truth
azimuth is below a certain threshold, the viewpoint is correct.
The baseline methods V-DPM~\cite{Xiang14} and
DPM-VOC+VP~\cite{Pepik12}) reported on the PASCAL3D+ dataset are
variants of DPM~\cite{Felzenszwalb10} where each component of DPM
account for various azimuths. Thus V-DPM and VOC-DPM provide discrete
azimuth only whereas our method provides 3D viewpoint (yaw, pitch,
roll), CAD instance (model index, rendering, depth) and focal length.
%
\begin{figure}[t]
 \begin{center}
    \setlength\tabcolsep{0pt}
    \begin{tabular}{ccc}
    % \includegraphics[width=0.9\linewidth]{tuning} 
   \includegraphics[width=0.33\linewidth]{tuning/1.png} &
   \includegraphics[width=0.33\linewidth]{tuning/2.png} &
   \includegraphics[width=0.33\linewidth]{tuning/3.png} \\[-5pt]
%   (a) & (b) & (c)\\
   \includegraphics[width=0.33\linewidth]{tuning/4.png} &
   \includegraphics[width=0.33\linewidth]{tuning/5.png} &
   \includegraphics[width=0.33\linewidth]{tuning/6.png} \\[-5pt]
%   (d) & (e) & (f)\\
   \end{tabular}
 \end{center}
 \caption{Effect of fine tuning. (left) original image, (middle) initial detection, (right) continuous fine tuning}
 \label{fig:tuning}
\end{figure}

@@

\begin{figure}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{cc}
%  \hline
  \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn8_crop.png} \\   
  \includegraphics[width=0.49\linewidth]{car_cnn16_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn24_crop.png} \\   
%  \hline
\end{tabular}
\caption{Average Precision (AP) and Average Viewpoint Precision (AVP)
  and viewpoint confusion table on PASCAL 12 car validation set using
  R-CNN + Ours (full). From the top left, 4 views, 8 views, 16 views
  and 24 views.}
 % Since our method only augment the object detection,
 %  the AP remains the same for all cases. As we increase the viewpoint
 %  estimation, the AVP decreases. Note that since we estimate null
 %  viewpoint if our method fails to find match, there are more 0
 %  viewpoint predictions (top row of confusion matrices) }
  \label{fig:car_cnn_ap}
\end{figure}

>>>>

\paragraph{Results.}
Tab.~\ref{tab:3dobject} gives the corresponding results, comparing our
method to two recent state-of-the-art baselines, the aspect layout
model (ALM~\cite{Xiang12}), and the
DPM-VOC+VP~\cite{Pepik12}. Fig.~\ref{fig:3dobject} gives
qualitative results.

@@

To show such ability, we evaluate our method on the PASCAL3D+
dataset~\cite{Xiang14}. This dataset augments PASCAL 2012 images with
high quality viewpoint annotations thus is ideal to measure pose
estimation. The dataset proposes new metric called Average Viewpoint
Precision (AVP) where it measures the area under viewpoint precision
and detection recall curve. The viewpoints is measured by azimuth
similarity. If the distance between predicted azimuth and ground truth
azimuth is below a certain threshold, the viewpoint is correct.
The baseline methods V-DPM~\cite{Xiang14} and
DPM-VOC+VP~\cite{Pepik12}) reported on the PASCAL3D+ dataset are
variants of DPM~\cite{Felzenszwalb10} where each component of DPM
account for various azimuths. Thus V-DPM and VOC-DPM provide discrete
azimuth only whereas our method provides 3D viewpoint (yaw, pitch,
roll), CAD instance (model index, rendering, depth) and focal length.
%
\begin{figure}[t]
 \begin{center}
    \setlength\tabcolsep{0pt}
    \begin{tabular}{ccc}
    % \includegraphics[width=0.9\linewidth]{tuning} 
   \includegraphics[width=0.33\linewidth]{tuning/1.png} &
   \includegraphics[width=0.33\linewidth]{tuning/2.png} &
   \includegraphics[width=0.33\linewidth]{tuning/3.png} \\[-5pt]
%   (a) & (b) & (c)\\
   \includegraphics[width=0.33\linewidth]{tuning/4.png} &
   \includegraphics[width=0.33\linewidth]{tuning/5.png} &
   \includegraphics[width=0.33\linewidth]{tuning/6.png} \\[-5pt]
%   (d) & (e) & (f)\\
   \end{tabular}
 \end{center}
 \caption{Effect of fine tuning. (left) original image, (middle) initial detection, (right) continuous fine tuning using Single-Component Metropolis Hastings}
 \label{fig:tuning}
\end{figure}

@@

\begin{figure}[h]
\setlength\tabcolsep{1pt}
\centering
\begin{tabular}{cc}
%  \hline
  \includegraphics[width=0.49\linewidth]{car_cnn4_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn8_crop.png} \\   
  \includegraphics[width=0.49\linewidth]{car_cnn16_crop.png} &   
  \includegraphics[width=0.49\linewidth]{car_cnn24_crop.png} \\   
%  \hline
\end{tabular}
\caption{Average Precision (AP)(red) and Average Viewpoint Precision (AVP)(green)
  and viewpoint confusion table on PASCAL 12 car validation set using
  R-CNN + Ours (full). From the top left, 4 views, 8 views, 16 views
  and 24 views.}
 % Since our method only augment the object detection,
 %  the AP remains the same for all cases. As we increase the viewpoint
 %  estimation, the AVP decreases. Note that since we estimate null
 %  viewpoint if our method fails to find match, there are more 0
 %  viewpoint predictions (top row of confusion matrices) }
  \label{fig:car_cnn_ap}
\end{figure}

### 2014-11-14 intro.tex
spell check
number

In this paper, we propose a novel method for 2D-3D alignment of
exemplar CAD models to real-world images that circumvents the need for
calibration, and greatly enhances the scalability of WHO. As a
result, we can render novel views and train corresponding exemplar
models {\em on the fly}, without the need for offline processing. As a
by-product, we can formulate the alignment problem as a parameter
search in a continuous pose space, consisting of yaw, pitch and roll, resulting in truly continuous pose estimates, which
we implement using MCMC sampling.
%  require a large number of rendering and 2D
% templates for each of the CAD model with specific viewpoint. Since
% there are so many templates that it becomes almost impossible to get
% all the true positive image from training data. Instead \cite{Aubry14,
%   Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to
% make templates more discriminative. Then calibration is done on a
% small training dataset.
%
% Although whitening to create template is faster than some of
% instance-level matching algorithms such as training Exemplar-SVM
% \cite{Malisiewicz11} or complicated models such as LEVAN
% \cite{Divvala14}, whitening and calibration large number of templates
% takes very long time. Also, once the fixed discrete viewpoint
% templates have been made and calibrated, it is difficult to fine-tune
% the prediction made using the large collection of templates.

@@

First, we present a novel method for training exemplar models from
rendered 3D CAD data {\em on the fly}, enabled by a novel variant of
WHO, termed NZ-WHO, and making efficient use of the specific
characteristics of rendered images. To our knowledge, our method
constitutes the first attempt to simultaneously render and train
exemplar detectors on the fly.
% In our paper, we present Non-Zero Whiten Histograms of Orientations
% (NZ-WHO) to dramatically speed up the template generation and get rid
% of time consuming calibration and yet achieves performance on par with
% calibrated templates. First, we will present NZ-WHO is more
% discriminative than WHO and introduce Conjugate Gradient method to
% speed up the whitening and create a high resolution template in just
% 80 milliseconds. Also, using this fast NZ-WHO template generation, we
% present \textbf{on-the-fly} template generation to fine tune an
% initial pose estimation to continuously refine translation, viewpoints
% (yaw, roll, pitch) and focal length.

Second, we show to enrich the output of an existing object class
detector, such as the DPM~\cite{Felzenszwalb10} or the
R-CNN~\cite{Girshick14} with additional 3D information, applying our
method to candidate detections provided by the respective detector. As
a result, we can refine the original detections with additional
estimates of 3D continuous pose and a 3D CAD model exemplar.

And third, we give an in-depth experimental study that demonstrates
the effectiveness of our approach on a standard benchmark for
object detection and viewpoint estimation~\cite{Xiang14}.

>>>>

In this paper, we propose a novel method for 2D-3D alignment of
exemplar CAD models to real-world images that circumvents the need for
calibration, and greatly enhances the scalability of WHO. As a
result, we can render novel views and train corresponding exemplar
models {\em on the fly}, without the need for offline processing and we call thses NZ-WHO templates \ref{fig:front}. As a
by-product, we can formulate the alignment problem as a parameter
search in a continuous pose space, consisting of yaw, pitch and roll, resulting in truly continuous pose estimates, which
we implement using MCMC sampling.
%  require a large number of rendering and 2D
% templates for each of the CAD model with specific viewpoint. Since
% there are so many templates that it becomes almost impossible to get
% all the true positive image from training data. Instead \cite{Aubry14,
%   Lim14} used whitening as a preprocessing stage \cite{Hariharan12} to
% make templates more discriminative. Then calibration is done on a
% small training dataset.
%
% Although whitening to create template is faster than some of
% instance-level matching algorithms such as training Exemplar-SVM
% \cite{Malisiewicz11} or complicated models such as LEVAN
% \cite{Divvala14}, whitening and calibration large number of templates
% takes very long time. Also, once the fixed discrete viewpoint
% templates have been made and calibrated, it is difficult to fine-tune
% the prediction made using the large collection of templates.

@@

First, we present a novel method for training exemplar models from
rendered 3D CAD data {\em on the fly}, enabled by a novel variant of
WHO, termed NZ-WHO, and making efficient use of the specific
characteristics of rendered images. To our knowledge, our method
constitutes the first attempt to simultaneously render and train
exemplar detectors on the fly.
% In our paper, we present Non-Zero Whiten Histograms of Orientations
% (NZ-WHO) to dramatically speed up the template generation and get rid
% of time consuming calibration and yet achieves performance on par with
% calibrated templates. First, we will present NZ-WHO is more
% discriminative than WHO and introduce Conjugate Gradient method to
% speed up the whitening and create a high resolution template in just
% 80 milliseconds. Also, using this fast NZ-WHO template generation, we
% present \textbf{on-the-fly} template generation to fine tune an
% initial pose estimation to continuously refine translation, viewpoints
% (yaw, roll, pitch) and focal length.
%
Second, we show to enrich the output of an existing object class
detector, such as the DPM~\cite{Felzenszwalb10} or the
R-CNN~\cite{Girshick14} with additional 3D information, applying our
method to candidate detections provided by the respective detector. As
a result, we can refine the original detections with additional
estimates of 3D continuous pose and a 3D CAD model exemplar.
%
And third, we give an in-depth experimental study that demonstrates
the effectiveness of our approach on a standard benchmark for
object detection and viewpoint estimation~\cite{Xiang14}.
